---
title: "Does Physical Restraint Use Prevent Falls in Nursing Homes? Evidence from a Decade of Quality Monitoring Data"
author:
  - name: Ivan Marino
    email: ivan.marino@upipa.tn.it
    roles: [conceptualization, data curation, analysis, methodology, resources, software, validation, visualization, writing]
    affiliation:
      - ref: upipa
  - name: Marco Pagani
    email: pagani.marco1.2@gmail.com
    roles: [conceptualization, investigation]
  - name: Eleonora Negri
    email: eleonora.negri@upipa.tn.it
    roles: [conceptualization, funding]
    affiliation:
      - ref: upipa
  - name: Massimo Giordani
    email: direttore@upipa.tn.it
    roles: [conceptualization, funding]
    affiliation:
      - ref: upipa
  - name: Marianna Baggia
    email: marianna.baggia@upipa.tn.it
    roles: [conceptualization, funding]
    affiliation:
      - ref: upipa
  - name: Massimiliano Vario
    email: massimiliano.vario@provincia.tn.it
    roles: [conceptualization]
    affiliation:
      - ref: pat
  - name: Emanuele Torri
    email: emanuele.torri@asuit.tn.it
    roles: [conceptualization]
    affiliation:
      - ref: asuit
affiliations:
  - id: upipa
    name: UPIPA — Unione Provinciale Istituzioni per l'Assistenza
  - id: pat
    name: Provincia Autonoma di Trento
  - id: asuit
    name: Azienda Sanitaria Universitaria Integrata del Trentino
format:
  html:
    toc: true
    self-contained: true
bibliography: references.bib
execute:
  echo: false
abstract: |
    **Background.** Physical restraint use in nursing homes is widely practiced,
    often justified by fall prevention, yet its effectiveness is contested. Most
    evidence comes from short trials or cross-sectional comparisons; longitudinal
    evidence across many facilities is scarce.

    **Methods.** We analyzed ten years (2016–2025) of quality-monitoring data from
    36 nursing homes in Trento, Italy (Indicare Salute Lab, UPIPA), pairing monthly
    restraint prevalence with three nested fall indicators (total falls, falls with
    any outcome, falls with major outcome). We fitted a Bayesian hierarchical model
    with a collapsed binomial likelihood: falls given the observed restraint count,
    with the nested outcomes factorized as Binomial(fall) × Multinomial(outcome |
    fall). Facility–sector pairs received their own restraint time trends and
    partially pooled fall rates (Beta hierarchy) and outcome shares
    (logistic-normal hierarchy). Model development used Bayes factors and
    posterior predictive checks.

    **Results.** The restraint–fall association was strongly heterogeneous across
    the `r if (!exists("K")) invisible(source("compute-results.R")); K`
    facility–sector pairs: about `r n_fall["benefit"]` showed credible
    benefit, `r n_fall["harm"]` credible harm, and `r n_fall["uncertain"]` were
    uncertain. For a new, unobserved pair, the posterior predictive probability
    of benefit was `r round(100 * p_new_benefit)`%. On average, restrained
    residents fell slightly less (δ = `r fmt(mean(delta_fall))`, 95% HDI
    `r fmt_hdi(delta_fall)`), but there was no evidence of benefit on
    major-outcome falls (δ = `r fmt(mean(delta_major))`, 95% HDI
    `r fmt_hdi(delta_major)`), and on minor-outcome falls more pairs showed
    credible harm (`r n_minor["harm"]`) than benefit (`r n_minor["benefit"]`).

    **Conclusions.** The effect of physical restraint on falls is real but not
    generalizable: its sign and magnitude vary unpredictably across facilities, and
    there is no meaningful evidence of benefit where it matters most — falls with
    major outcomes. Effectiveness as a fall-prevention strategy should be evaluated
    case by case.
keywords:
  - physical restraint
  - falls
  - nursing homes
  - Bayesian hierarchical model
  - quality monitoring
  - ecological study
---

```{r}
#| label: setup
#| include: false

# Compute all manuscript numbers from the posterior draws. When rendering, the
# first inline expression in the YAML abstract has already sourced this file
# (knitr evaluates YAML inline code before any chunk); the guard makes both
# entry points idempotent.
if (!exists("K")) source("compute-results.R")
```

# Background

Physical restraint use in nursing homes remains common despite longstanding
ethical and clinical controversy [@hakverdiogluyönt2023]. The most frequently
cited justification is the prevention of falls and fall-related injuries, yet
the evidence base is weak and contested: a Cochrane review of interventions
to reduce restraint use in long-term care found that restraint prevalence can
be reduced without increasing falls or fall-related injuries [@möhler2023] —
a finding difficult to reconcile with a protective effect of restraint.

The available evidence base is small and of low certainty: systematic reviews
have repeatedly characterized it as limited and inconclusive [@möhler2023;
@sze2012; @hakverdiogluyönt2023], and the primary studies are typically
short-term and compare restrained and non-restrained residents within single
facilities or small facility samples [@tinetti1992; @capezuti1996;
@fernandezibanez2020]. Two gaps remain.
First, few studies observe the same facilities longitudinally over many
years, so secular trends and within-facility variation are poorly understood.
Second, falls are often analyzed as a single, undifferentiated outcome, and
even when severity is recorded, classification is inconsistent and major
injuries are substantially underreported [@sanghavi2020] — although the
clinical stakes differ enormously between a fall without consequences and one
causing fracture or serious injury. The few studies that distinguish
injurious falls have found no protective effect of restraint — and possibly
more serious fall-related injuries [@tinetti1992; @capezuti1996]. If
restraint prevents only clinically irrelevant falls, its use as a preventive
strategy loses justification.

We address both gaps using a decade of quality-monitoring data from the
province of Trento, Italy, analyzing total falls alongside two nested
severity outcomes in a unified Bayesian hierarchical model.

# Methods

## Data

Data come from the **Indicare Salute Lab** quality-monitoring system (UPIPA),
covering 36 nursing homes in the province of Trento from 2016 to 2025. Each
record is a facility × care-sector × month combination reporting four
indicators: point prevalence of physical restraint on an index day (2.1), and
incidence of falls in the reference period — total falls (1.1), falls with any
recorded outcome (1.3), and falls with major outcome such as fractures (1.5).
The fall indicators are nested (1.5 ⊆ 1.3 ⊆ 1.1), so the outcome cells
(no outcome, minor, major, not fallen) form a multinomial vector over residents
by successive differences.

The severity classification is defined by the monitoring protocol. Falls
*without outcome* produced no harm of any kind. Falls with *minor outcome* are
injuries managed within the nursing home (abrasions, bruises, excoriations);
falls that required a diagnostic workup but resulted in no fracture are also
classified as minor. Falls with *major outcome* produced serious injuries or
fractures requiring diagnostic assessment, and also include loss of
consciousness or a change in the resident's physical or mental state. When a
single fall has more than one outcome, only the most severe is recorded.

The term *sector* requires clarification. Facilities may partition the data they
enter on the Indicare Salute Lab platform into autonomously defined sectors,
with no constraint on the level of the partition. When a facility comprises
multiple care homes, the typical — and recommended — partition is one sector
per home, with data entered separately for each; however, the subdivision is
purely nominal, and a facility could equally well define sectors as, say,
floors of a single building. Throughout, we therefore treat the
facility–sector pair as the analysis unit, understood as the level at which
the facility chose to organize its own reporting, rather than as a
standardized organizational entity. The analysis set comprises 2,524 records with both
restraint and fall data, plus partially observed records contributing marginal
information (242 restraint-only, 419 falls-only). Facility identifiers were
anonymized prior to analysis.

## Statistical model

Let $X$ be the number of restrained residents out of $n_x$ observed for
restraint, and $Y$ the number of residents who fell out of $n_y$ observed for
falls, in facility–sector pair $k$ at time $t$. We use a collapsed likelihood
that conditions falls on the observed restraint count:

$$
X \sim \text{Binomial}(n_x, p_k), \qquad
Y \mid X \sim \text{Binomial}\!\left(n_y,\; \bar p_k\right), \quad
\bar p_k = \frac{X}{n_x}\, q_k + \left(1 - \frac{X}{n_x}\right) r_k
$$

where $q_k$ and $r_k$ are the fall probabilities for restrained and
non-restrained residents. This mean-matched binomial replaces the exact
bivariate-binomial convolution; it was validated against the exact model
(nearly identical posteriors, ~10× faster sampling). Restraint prevalence
follows a per-pair quadratic time trend on the logit scale,
$\text{logit}(p_k) = \beta_k + \alpha_k t + \gamma_k t_2$, with $t_2$ the
orthogonalized, standardized quadratic term.

The three fall outcomes are modeled jointly through the four disjoint,
exhaustive outcome cells defined in the Data section: fall without outcome,
fall with minor outcome, fall with major outcome, and no fall. For a resident
of pair $k$, the cell probabilities under restraint and non-restraint are

$$
\mathbf{q}_k = \big(q_k\, s_{q,k1},\; q_k\, s_{q,k2},\; q_k\, s_{q,k3},\; 1 - q_k\big),
\qquad
\mathbf{r}_k = \big(r_k\, s_{r,k1},\; r_k\, s_{r,k2},\; r_k\, s_{r,k3},\; 1 - r_k\big),
$$

where $q_k$ and $r_k$ are the probabilities of falling and
$\mathbf{s}_{q,k} = (s_{q,k1}, s_{q,k2}, s_{q,k3})$ and
$\mathbf{s}_{r,k} = (s_{r,k1}, s_{r,k2}, s_{r,k3})$ are the shares of the three
outcome cells *conditional on a fall having occurred* (each summing to one).
Given the observed restraint count $X$, the multinomial count vector
$\mathbf{c} = (n_{1.1} - n_{1.3},\; n_{1.3} - n_{1.5},\; n_{1.5},\; n_y - n_{1.1})$
then follows

$$
\mathbf{c} \mid X \sim \text{Multinomial}\!\left(n_y,\; \bar{\mathbf{p}}_k\right),
\qquad
\bar{\mathbf{p}}_k = \frac{X}{n_x}\,\mathbf{q}_k + \left(1 - \frac{X}{n_x}\right)\mathbf{r}_k .
$$

This factorization — a binomial on the fall margin times a multinomial on the
outcome shares given a fall — is exact: the cells are disjoint by
construction, so no independence assumption across outcomes is needed.

Both sets of parameters are partially pooled across pairs. The fall rates
follow a Beta hierarchy with weakly informative exponential hyperpriors,

$$
q_k \sim \text{Beta}(a_q, b_q), \qquad r_k \sim \text{Beta}(a_r, b_r),
\qquad a_q, b_q, a_r, b_r \stackrel{\text{iid}}{\sim} \text{Exponential}(1),
$$

and the outcome shares follow a logistic-normal hierarchy, componentwise over
the three cells $m = 1, 2, 3$:

$$
\mathbf{s}_{q,k} = \operatorname{softmax}(\boldsymbol\eta_{q,k}),
\qquad
\eta_{q,km} \sim \text{Normal}(\mu_{qm},\, \sigma_{qm}),
\\
\mu_{qm} \sim \text{Normal}(0, 2),
\quad
\sigma_{qm} \sim \text{Exponential}(1),
$$

and identically for $\mathbf{s}_{r,k}$ with hyperparameters
$\boldsymbol\mu_r, \boldsymbol\sigma_r$. The model is fitted in non-centered
form, $\boldsymbol\eta_{q,k} = \boldsymbol\mu_q + \boldsymbol\sigma_q \odot
\mathbf{z}_{q,k}$ with $\mathbf{z}_{q,k} \sim \text{Normal}(\mathbf{0},
\mathbf{I})$, because a Dirichlet hierarchy on the shares exhibited
pathological sampling geometry at the boundary of the simplex. Having
documented substantial between-facility heterogeneity in fall rates, we
extended the same hierarchical structure to all levels of the model for
coherence, avoiding homogeneity assumptions not supported by the data.

```{r}
#| label: ppc-concordance
#| include: false

# Posterior predictive concordance: fraction of observations covered by their
# 95% predictive interval. Requires the full published fit (with per-
# observation predictive replications); the 210 MB file is not shipped with
# the package — only the light draws are (see ?load_fit) — so this chunk needs
# the local file.
fit_full_path <- c(
  file.path("..", "inst", "extdata", "fit_multinomial_fac_sec_quad.rds"),
  file.path("inst", "extdata", "fit_multinomial_fac_sec_quad.rds")
)
fit_full_path <- fit_full_path[file.exists(fit_full_path)][1]
if (is.na(fit_full_path)) {
  stop(
    "Full M12 fit not found (expected at inst/extdata/",
    "fit_multinomial_fac_sec_quad.rds). The PPC concordance values cannot ",
    "be computed from the light shipped draws."
  )
}
fit_full <- readRDS(fit_full_path)$fit
sd_multi <- prepare_model_data()$stan_data

# Fraction of observations covered by their 95% predictive interval
concordance <- function(obs, sims) {
  lo <- apply(sims, 2, quantile, 0.025)
  hi <- apply(sims, 2, quantile, 0.975)
  mean(obs >= lo & obs <= hi)
}

# Restraint and total falls: group observations as both / restraint-only /
# falls-only, the ordering reproduced by the model's generated quantities
wide <- restraints_falls |>
  dplyr::filter(indicatore %in% c(
    "2.1 Persone soggette a contenzione fisica",
    "1.1 Residenti caduti nel periodo di riferimento"
  )) |>
  dplyr::mutate(
    tipo = ifelse(grepl("contenzione", indicatore), "restr", "falls")
  ) |>
  dplyr::select(anno, mese, ente, id_settore, tipo, n, d) |>
  tidyr::pivot_wider(names_from = tipo, values_from = c(n, d))

has_restr <- !is.na(wide$n_restr) & !is.na(wide$d_restr)
has_falls <- !is.na(wide$n_falls) & !is.na(wide$d_falls)
both   <- wide[has_restr & has_falls, ]
x_only <- wide[has_restr & !has_falls, ]
y_only <- wide[!has_restr & has_falls, ]

obs_x <- c(as.integer(both$n_restr), as.integer(x_only$n_restr))
obs_y <- c(as.integer(both$n_falls), as.integer(y_only$n_falls))
pred_x <- as.matrix(fit_full$draws(c("x_rep", "x_only_rep"), format = "matrix"))
pred_y <- as.matrix(fit_full$draws(c("y_rep", "y_only_rep"), format = "matrix"))

conc_x <- concordance(obs_x, pred_x)
conc_y <- concordance(obs_y, pred_y)

# Outcome cells: the marginals of the multinomial are binomial, so indicator
# 1.3 (minor + major) and 1.5 (major) are simulated binomially on the
# multi-outcome records; the fall probability cancels out of the factorization
qf <- as.matrix(fit_full$draws("q_fall", format = "matrix"))
rf <- as.matrix(fit_full$draws("r_fall", format = "matrix"))
sq <- as.matrix(fit_full$draws("s_q", format = "matrix"))
sr <- as.matrix(fit_full$draws("s_r", format = "matrix"))

K <- sd_multi$K
kk <- sd_multi$fs_multi
nx <- sd_multi$nx_multi
frac <- ifelse(nx > 0, sd_multi$x_multi / nx, 0)
n_y <- sd_multi$n_y_multi
obs_13 <- sd_multi$c_multi[, 2] + sd_multi$c_multi[, 3]
obs_15 <- sd_multi$c_multi[, 3]

# In the flattened s_q/s_r draws, pair k varies fastest within cell m:
# cell m of pair k is column (m - 1) * K + k
p13 <- sweep(qf[, kk] * (sq[, K + kk] + sq[, 2 * K + kk]), 2, frac, `*`) +
       sweep(rf[, kk] * (sr[, K + kk] + sr[, 2 * K + kk]), 2, 1 - frac, `*`)
p15 <- sweep(qf[, kk] * sq[, 2 * K + kk], 2, frac, `*`) +
       sweep(rf[, kk] * sr[, 2 * K + kk], 2, 1 - frac, `*`)

nd <- nrow(p13)
set.seed(975059978)
n13_sim <- matrix(
  rbinom(length(p13), rep(n_y, each = nd), p13), nd
)
n15_sim <- matrix(
  rbinom(length(p15), rep(n_y, each = nd), p15), nd
)

conc_13 <- concordance(obs_13, n13_sim)
conc_15 <- concordance(obs_15, n15_sim)
```

## Estimation and model development

Models were fitted with NUTS in Stan (via cmdstanr), 4 chains with 1,000
warmup and 1,000 sampling iterations each (4,000 posterior draws retained). Twelve candidate specifications were compared during development
using Bayes factors (bridge sampling) where likelihoods were comparable, and
posterior predictive checks (concordance of 95% predictive intervals with
observations) throughout. The final model achieved near-perfect concordance on
restraint (`r fmt(100 * conc_x, 1)`%) and total falls
(`r fmt(100 * conc_y, 1)`%), and conservative coverage on the sparser outcome
indicators (`r fmt(100 * conc_13, 1)`% and `r fmt(100 * conc_15, 1)`%).

## Estimands

We report absolute differences in fall probabilities between restrained and
non-restrained residents (δ), at three levels: the realized mean across
observed pairs, the population mean under the hierarchy, and the posterior
predictive distribution for a new, unobserved pair (including the probability
of any benefit). Relative effects are summarized by medians, because the
posterior mean of the population-level ratio does not exist (the posterior of
the Beta shape parameter retains mass below 1, where the expectation diverges).
The same analysis is reported per outcome cell, both per resident and
conditional on a fall having occurred.

# Results

## Overall association

On average across observed pairs, restrained residents fell slightly less than
non-restrained ones (δ = `r fmt(mean(delta_fall))`, 95% HDI
`r fmt_hdi(delta_fall)`; RR = `r fmt(median(rr_fall), 2)`, 95% HDI
`r fmt_hdi(rr_fall, 2)`). The population-level mean difference was negative with
`r round(100 * p_pop_neg)`% posterior probability.

## Heterogeneity across facilities

The association was strongly heterogeneous across the `r K` facility–sector
pairs (@tbl-delta). About `r n_fall["benefit"]` pairs showed credible benefit
(P(δ < 0) ≥ 0.95), `r n_fall["harm"]` credible harm (P(δ < 0) ≤ 0.05, up to δ =
+`r fmt(max_harm_delta, 2)`), and `r n_fall["uncertain"]` were uncertain. For a
new, unobserved pair, the posterior predictive probability of benefit was
`r round(100 * p_new_benefit)`% (median risk ratio `r fmt(rr_new_med, 2)`, with
a very wide predictive interval). The heterogeneity was concentrated among
restrained residents: between-pair variability of $q_k$ far exceeded that of
$r_k$ (logit-scale SD `r fmt(sd_logit_q, 2)` vs `r fmt(sd_logit_r, 2)`). The delta was not associated with the facility's
observed restraint rate, a proxy for local restraint policy.

```{r}
#| label: tbl-delta
#| tbl-cap: "Posterior mean difference in fall probability between restrained and non-restrained residents (delta = q − r) per facility–sector pair, with 95% highest density interval and the posterior probability of a negative delta. Pairs are anonymized (facility_sector). Computed live from the posterior draws shipped with the companion package."
#| echo: false
#| eval: true
#| message: false
#| warning: false

library(restraintsfalls)

draws <- load_fit()
pair_labels <- prepare_model_data()$meta$pair_labels

qf <- as.matrix(posterior::as_draws_matrix(posterior::subset_draws(
  draws,
  variable = "q_fall"
)))
rf <- as.matrix(posterior::as_draws_matrix(posterior::subset_draws(
  draws,
  variable = "r_fall"
)))
delta <- qf - rf

tab <- apply(delta, 2, function(v) {
  h <- bayestestR::hdi(v)
  c(
    delta_mean = mean(v),
    hdi_lo = h$CI_low,
    hdi_hi = h$CI_high,
    p_neg = mean(v < 0)
  )
}) |>
  t() |>
  as.data.frame() |>
  round(3)

tab <- data.frame(Pair = pair_labels, tab, row.names = NULL)
names(tab) <- c("Pair", "Mean delta", "HDI lower", "HDI upper", "P(delta < 0)")
knitr::kable(tab)
```

<!-- TODO: 47 righe sono tante per il testo principale — valutare se spostare
la tabella completa in supplementary e tenere nel testo solo una figura
(forest plot dei delta per coppia) -->

## Severity-specific outcomes

For major-outcome falls — the clinically important events — the average effect
was compatible with zero (δ = `r fmt(mean(delta_major))`, 95% HDI
`r fmt_hdi(delta_major)`) and predictive evidence of benefit was weak (P =
`r fmt(p_major_new_red, 2)` for a new pair). For minor-outcome falls, more
pairs showed credible harm (`r n_minor["harm"]`) than credible benefit
(`r n_minor["benefit"]`), and the predictive probability of reduction was
`r fmt(p_minor_new_red, 2)`. Conditional on a fall having occurred, the share
of minor outcomes tended to increase with restraint
(`r round(100 * p_share_minor_incr)`% posterior probability), while the share
of major outcomes was unchanged (`r round(100 * p_share_major_incr)`%).

# Discussion

## Principal findings

Across a decade of monitoring data, physical restraint was associated with a
modest average reduction in falls, but the association was strongly
heterogeneous: it reversed sign in a substantial minority of facility–sector
pairs, and the probability that a new facility would see any benefit was barely
above chance. Critically, there was no evidence of benefit on falls with major
outcomes — the events that restraint is meant to prevent — and on
minor-outcome falls the balance tilted toward harm.

## The heterogeneity is the finding

The heterogeneity was concentrated in the fall rates of restrained residents,
while the baseline risk of non-restrained residents was comparatively stable
across facilities. This pattern suggests that what differs between facilities
is not the residents' underlying risk but what happens to restrained
residents — plausibly local restraint practices or selection of who is
restrained. Our ecological design cannot distinguish these mechanisms, and the
heterogeneity was not explained by the facility's restraint intensity.

## Relation to previous work

Our findings are consistent with the Cochrane review's finding that reducing
restraint use does not increase falls [@möhler2023], and add a longitudinal,
multi-facility perspective: even where an average association exists, it does
not generalize. The primary studies that distinguished injurious falls found
restraint associated with more, not fewer, serious fall-related injuries
[@tinetti1992], and no protective effect in the resident subgroups most
likely to be restrained [@capezuti1996; @fernandezibanez2020] — consistent
with the credible-harm pairs in our data. Studies reporting
protective average effects may be pooling over sign-varying facility effects.
<!-- TODO: additional references (falls in NH, restraint prevalence, ecological bias) -->

## The "fewer seriously injured fallers" defense fails

A possible defense of restraint is that even if those who fall get hurt more
often, the total number of seriously injured fallers decreases. Our
decomposition tests exactly this: the per-resident rate of major-outcome falls
did not decrease (P = `r fmt(p_major_new_red, 2)`, HDI spanning zero), and for
minor outcomes the predictive mean was slightly positive
(`r fmt(mean(delta_minor_new))`). Granting the premise does not rescue the
conclusion.

## Limitations

The design is ecological: the unit is the facility–month, not the resident, so
reverse causation cannot be excluded (a fall may reduce the subsequent
probability of restraint, generating an artificial protective association) and
no adjustment for case-mix or staffing was possible. Major-outcome cells are
sparse, limiting per-pair inference (43 of 47 pairs unclassifiable) and
producing conservative predictive intervals. The sparsity is likely compounded
by measurement: major-injury falls are substantially underreported in
quality-monitoring data [@sanghavi2020]. Because such underreporting plausibly
affects restrained and non-restrained residents similarly, the contrasts
(deltas) are more robust to it than the absolute rates, which are probably
underestimated. The collapsed likelihood is an
approximation, albeit validated against the exact model.

Two measurement limitations concern how facilities organize and define their
own data. First, facility–sector pairs reflect heterogeneous partitioning
choices: because sectors are autonomously defined (typically one per care home,
but potentially any subdivision such as floors of a single building), pairs are
not a standardized organizational unit, and part of the observed between-pair
heterogeneity may reflect different partitioning conventions rather than
genuine differences in practice. Second, facilities vary somewhat in what they
count as physical restraint — for instance, some do not report restraint
explicitly requested by the resident — introducing a presumably small
variability in the restraint indicator across facilities. Within a facility,
however, the working definition of restraint is constant over time, so the
estimated restraint–fall contrasts remain internally valid for each pair; the
between-facility definitional variability may instead contribute to the
observed heterogeneity of effects across pairs. We do not consider this a
material threat to the validity of our findings. Finally, the 36
facilities come from a single Italian province, and the predictive statements
concern that population.

## Implications

For practice: restraint should not be assumed to prevent falls, and any
facility-level evaluation of restraint policies should use the facility's own
data rather than assumed average effects. For research: individual-level data
linking restraint episodes to subsequent falls, with case-mix adjustment, are
needed to separate the causal directions.

# Conclusions

The effect of physical restraint on falls is real but not generalizable: its
sign and magnitude vary unpredictably across facilities, and there is no
meaningful evidence of benefit on the falls that matter most. Effectiveness as
a fall-prevention strategy should be evaluated case by case, based on the
characteristics of each facility, and confirmed with individual-level data.

# Declarations

**Ethics approval and consent to participate.** <!-- TODO: ethics statement — aggregated anonymized monitoring data; verify need for ethics approval / delibera reference -->

**Consent for publication.** Not applicable.

**Availability of data and materials.** The analysis code is available at
https://github.com/upipa/restraints-falls-nh. The data are quality-monitoring
records of UPIPA member facilities and are not publicly available.
<!-- TODO: verify data-sharing statement with UPIPA -->

**Competing interests.** The authors declare no competing interests.

**Funding.** <!-- TODO -->

**Authors' contributions.** <!-- TODO -->

**Acknowledgements.** <!-- TODO -->

# References
