---
title: "Does Physical Restraint Use Prevent Falls in Nursing Homes?"
subtitle: "Evidence from a Decade of Quality Monitoring Data"
vignette: >
  %\VignetteIndexEntry{Does Physical Restraint Use Prevent Falls in Nursing Homes?}
  %\VignetteEngine{quarto::html}
  %\VignetteEncoding{UTF-8}
---

```{r}
#| label: setup
#| include: false
library(restraintsfalls)
```

## Background

Physical restraint use in nursing homes is a common but controversial practice.
One of the most frequently cited justifications is fall prevention. This analysis
examines whether facility-level restraint prevalence is associated with lower
fall rates, using longitudinal data from 2016 to 2025 across nursing homes in
the province of Trento, Italy.

## Data

Data come from the **Indicare Salute Lab** quality monitoring system. Each
observation represents a facility × care-sector × month combination, pairing
the restraint indicator (2.1, point prevalence on the index day) with three
nested fall indicators: total falls (1.1), falls with any outcome (1.3), and
falls with major outcome such as fractures (1.5). The nesting
($1.5 \subseteq 1.3 \subseteq 1.1$) allows the outcome cells to be modeled as a
single multinomial vector over residents.

## Model

The final model is a Bayesian hierarchical model with a collapsed likelihood.
Conditional on the observed restraint count $X$ in a facility–sector pair $k$:

$$
X \sim \text{Binomial}(n_x, p_k), \qquad
Y \mid X \sim \text{Binomial}\!\left(n_y,\; \bar p_k\right), \quad
\bar p_k = \frac{X}{n_x}\, q_k + \left(1 - \frac{X}{n_x}\right) r_k
$$

where $q_k$ and $r_k$ are the fall probabilities for restrained and
non-restrained residents. Fall outcomes are factorized exactly as
Binomial(fall) × Multinomial(outcome | fall), with outcome cells
(no outcome / minor / major). Restraint prevalence follows a per-pair
quadratic time trend on the logit scale (orthogonalized and standardized),
$\text{logit}(p_k) = \beta_k + \alpha_k t + \gamma_k t^2$; fall rates are
partially pooled across pairs via Beta hyperpriors, and outcome shares via a
non-centered logistic-normal hierarchy.

```{r}
#| label: reproduce-fit
#| eval: false
# The fitted model is not shipped (large file, ~6 h runtime). The analysis is
# fully reproducible from the packaged dataset with two function calls:
prep <- prepare_model_data()
fit <- fit_model(prepared = prep) # full fit; use quick = TRUE for a fast check

# The complete development workflow (all 12 model iterations, Bayes factors,
# posterior predictive checks) is in data-raw/model-development.qmd of the
# source repository.
```

## Results

The association between restraint and falls is **strongly heterogeneous**
across facility–sector pairs. Of the 47 pairs, about 15 show credible benefit
(restrained residents fall less), about 8 show credible harm, and the rest are
uncertain — the effect changes sign across facilities. For a new, unobserved
facility–sector pair, the posterior predictive probability of any benefit is
only about 61%.

For **major-outcome falls** (the clinically important ones), the average
effect is compatible with zero and predictive evidence of benefit is weak
(P ≈ 0.60). On falls with minor outcomes, more pairs show credible harm (10)
than credible benefit (6).

## Conclusions

The effect of physical restraint on falls is real but not generalizable: its
sign and magnitude vary unpredictably across facilities. There is no
meaningful evidence that restraint reduces the falls that matter most — those
with major outcomes. Effectiveness as a fall-prevention strategy should be
evaluated case by case, based on the characteristics of each facility, and
confirmed with individual-level data.
