---
title: "Does Physical Restraint Use Prevent Falls in Nursing Homes?"
subtitle: "Evidence from a Decade of Quality Monitoring Data"
vignette: >
  %\VignetteIndexEntry{Does Physical Restraint Use Prevent Falls in Nursing Homes?}
  %\VignetteEngine{quarto::html}
  %\VignetteEncoding{UTF-8}
---

```{r}
#| label: setup
#| include: false
library(restraintsfalls)
```

## Background

Physical restraint use in nursing homes is a common but controversial practice.
One of the most frequently cited justifications is fall prevention. This analysis
examines whether facility-level restraint prevalence is associated with lower
fall rates, using longitudinal data from 2016 to 2025 across nursing homes in
the province of Trento, Italy.

## Data

Data come from the **Indicare Salute Lab** quality monitoring system. Each
observation represents a facility-year combination, with indicators for
restraint prevalence and fall rates.

## Model

We use a Bayesian binomial model linking restraint prevalence to fall rates
on the logit scale:

$$
\text{logit}(q_i) = \alpha \cdot \text{logit}(p_i) + \beta + \gamma \cdot t_i
$$

where $p_i$ is the latent restraint prevalence, $q_i$ is the fall probability,
and $t_i$ is the year (centered).

```{r}
#| label: load-posteriors
posteriors_path <- system.file(
  "extdata",
  "posteriors.rds",
  package = "restraintsfalls"
)
if (file.exists(posteriors_path)) {
  posteriors <- readRDS(posteriors_path)
}
```

## Results

<!-- Results will be filled in once the final model is selected -->

## Conclusions

<!-- To be written -->
